The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-01-27 paper/sections/results.tex
finished the timing table
puft

%show stoppers
Finally we show a few additional examples, highlighting the ability of SEM to handle complex simulations involving deformation, contact and friction.
In \reffig{staypuft} we show two astronauts in jaunty space suits collide in zero gravity while in \reffig{starship} 
we show an animation of the Space-V starship landing on Mars in a graceful way.

\begin{figure*}[htp]
  \includegraphics[width=\textwidth,height=3in]{example-image-a}
  \caption{Two astronauts, in jaunty spacesuits collide while spacewalking in zero-g.}
  \label{fig:staypuft}
\end{figure*}

>>>>

%show stoppers
Finally we show a few additional examples, highlighting the ability of SEM to handle complex simulations involving deformation, contact and friction.
In \reffig{staypuft} we show two astronauts in jaunty space suits collide in zero gravity. 
SEM gracefully allows bounded discontinuities in simulation output to allow for rich motion. 
This is similar to Discontinous Galerkin approaches but in SEM this behavior is emerges from the kinematic model, rather than from additional flux terms~\cite{kaufmann2009flexible}.

In \reffig{starship} we show an animation of the Space-V starship landing on Mars in a graceful way.

\begin{figure*}[htp]
  \includegraphics[width=\textwidth]{figures/astronauts.pdf}
  \caption{Two astronauts, in jaunty spacesuits collide while spacewalking in zero-g. SEM correctly handles severely disconnected parts by correctly estimating elastic energy even in discontinuous regions.}
  \label{fig:staypuft}
\end{figure*}
